Supplement for: Carbon cycling in mature and regrowth forests globally

### 2021-01-25 manuscript/response_to_reviews.Rmd

## LETTER TO EDITOR:

Dear Editor:

We are please to submit a revised version of our manuscript, "Carbon cycling in mature and regrowth forests globally" (ERL-109898), for consideration for publication in *Environmental Research Letters*. We have addressed all points raised by the reviewers, as detailed below. The most substantive changes included the following:

- We changed the figure set in accordance with comments from R3. Specifically, we (1) added a schematic figure, somewhat in the style of @odum_strategy_1969, to help with conceptual framing of the review; (2) added a figure synthesizing changes in fluxes through time for each biome; (3) removed maps from age trend diagrams (maps still available in supplementary information), which makes the figures less busy/ easier to read; and (4) moved C cycle diagrams for young forests to the supplementary information.

### 2021-01-25 manuscript/ERL_global_C_SI.Rmd
change title to match online submission

---
title: "Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database"
output: 
  pdf_document:
    fig_caption: yes    
    toc: true # table of content true
    toc_depth: 2  
bibliography: references.bib
csl: environmental-research-letters.csl

>>>>

---
title: "Supplement for: Carbon cycling in mature and regrowth forests globally"
output: 
  pdf_document:
    fig_caption: yes    
    toc: true # table of content true
    toc_depth: 2  
bibliography: references.bib
csl: environmental-research-letters.csl
